### 2017-07-19 profiles_examples.Rmd
stubbed out print method; #14
Fix spacing
Add one prop bootstrap implementation to profiles example

One categorical (one proportion) (not yet implemented)

```
prof_small %>%
  specify(response = sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop")
```

>>>>

One categorical (one proportion)

```{r}
prof_small %>%
  specify(response = sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop", success = "f") %>% 
  visualize()
```
